---
title: "501/580 Kids Online - Attention Project"
author: "Kodie Vincent"
date: "2023-01-05"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60), tidy=TRUE, warning = FALSE, message = FALSE)
```

```{r}
#Load all required libraries

library("plyr")  
library("dplyr")
library("readr")  
library("readxl")
library("xlsx")
library("stringr")

```

## Load Files
Import files from selected participant and store in list of data frames.
Fields to be edited:

* file_path - change to the relevant participants file on the secure storage

```{r}
#Specify file path where excel files are stored 
file_path = "\\\\storage.hcs-wlg.otago.ac.nz/uow-ph-kidsonline/Dunedin Campus/2021 Scotts College Participants BORIS/Scots 13/Scots 13 EXCEL Export"

#Set as working directory 
setwd(file_path)

#Get each file making sure to get the entire file name
file_list <- list.files(path = file_path, pattern = '*.xlsx', full.names = T)

#Read in data from each file and store in list of data frames 
data <- lapply(file_list, function(x) read.xlsx(x, sheetIndex = 1))

```

## Cleaning Stage 1
Once complete we have a list of data frames we want to loop over each one in the list and perform some basic cleaning tasks.

* Remove empty rows
* Remove rows that are currently not used
* Set header row
* Add empty columns to populate
* End of first pre-processing for loop

```{r}

for (i in 1:length(data)){
  data[[i]] <- as.data.frame(data[i])
  data[[i]] <- data[[i]][!apply(data[[i]] == "", 1, all), ]
  data[[i]] <- data[[i]][!(data[[i]]$Observation.id=="Media file(s)" | data[[i]]$Observation.id=="variable" | data[[i]]$Observation.id=="independent variables" | data[[i]]$Observation.id=="Time offset (s)" ),]
  header <- data[[i]][4,]
  colnames(data[[i]]) <- header
  data[[i]]$Participant <- NA
  data[[i]]$Device <- NA
  data[[i]]$Recording_Day <- NA
  data[[i]]$Recording_Date <- NA
  data[[i]]$Recording_Time <- NA
  data[[i]]$Recording_Duration <- NA
}

```

## Cleaning Stage 2
Split description String that contains information about device, recording duration, recording time, date and day, device and participant and populate those fields.

```{r}

for (i in 1:length(data)){
  datdes <- data[[i]][3,2]
  dspace <- strsplit(datdes, " ")
  ddevice <- strsplit(dspace[[1]][1], "-")
  dpartic <- ddevice[[1]][1] 
  dddevice <- ddevice[[1]][2]
  ddate <- paste(dspace[[1]][2], dspace[[1]][3], sep=" ")
  dtime <- paste(dspace[[1]][4], dspace[[1]][5], sep=" ")
  dduration <- dspace[[1]][6]
  data[[i]]$Recording_Duration <- dduration
  data[[i]]$Recording_Time <- dtime
  data[[i]]$Recording_Date<- ddate
  data[[i]]$Device <- dddevice
  data[[i]]$Participant <- dpartic
  data[[i]] <- subset(data[[i]], data[[i]]$Time != "Time" & data[[i]]$Time != "Observation date" & data[[i]]$Time != "Player #1" & data[[i]]$Time != "Description")
  
}


```

## Cleaning Stage 3
Remove redundant rows and empty columns and bind individual excel files into one excel file then export to participant's file. 

Fields to be edited:

* write.xlsx - Change to the relevant participants file on the secure storage and name the export as "Participant Name Master"

```{r}

dataset <- bind_rows(data)

dataset <- select(dataset, -c("Subject", "Behavioral category", "Comment"))

```

```{r}

write.xlsx(dataset,  "\\\\storage.hcs-wlg.otago.ac.nz/uow-ph-kidsonline/Dunedin Campus/2021 Scotts College Participants BORIS/Scots 13/Scots 13 Cleaned.xlsx")

```

At the conclusion of this process the participants file structure should resemble the following, with all BORIS exports in a file named "Participant Name BORIS Excel Export" and the final file saved under the participants main file. 

![Participants Final File Structure](C:\Users\GGPC\OneDrive - University of Otago\INFO501 - Masters Thesis\participants_file)


